Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-06 talk/iwtc11/paper.tex
add all actionable reviewer comments to the paper

\newcommand\cfbolz[1]{\nb{CFB}{#1}}
\newcommand\arigo[1]{\nb{AR}{#1}}
\newcommand\fijal[1]{\nb{FIJAL}{#1}}
\newcommand\david[1]{\nb{DAVID}{#1}}
\newcommand\anto[1]{\nb{ANTO}{#1}}
\newcommand\reva[1]{\nb{Reviewer 1}{#1}}
\newcommand\revb[1]{\nb{Reviewer 2}{#1}}
\newcommand\revc[1]{\nb{Reviewer 3}{#1}}
\newcommand{\commentout}[1]{}
\newcommand{\ignore}[1]{} % {{\tt \small ignore(#1)}}

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\newcommand\cfbolz[1]{\nb{CFB}{#1}}
\newcommand\arigo[1]{\nb{AR}{#1}}
\newcommand\fijal[1]{\nb{FIJAL}{#1}}
\newcommand\david[1]{\nb{DAVID}{#1}}
\newcommand\anto[1]{\nb{ANTO}{#1}}
\newcommand\reva[1]{\nb{Reviewer 1}{#1}}
\newcommand\revb[1]{\nb{Reviewer 2}{#1}}
\newcommand\revc[1]{\nb{Reviewer 3}{#1}}
\newcommand\revd[1]{\nb{Reviewer 4}{#1}}
\newcommand{\commentout}[1]{}
\newcommand{\ignore}[1]{} % {{\tt \small ignore(#1)}}

@@

\reva{
You often use the word simple. While it might make sense to use it,
it exact meaning in that context remains unclear.
}

@@

\revc{
Don't break code listings across pages, as at the start of section 3.  It makes
them very hard to follow.
}

@@

\reva{
I think the motivation section is great, in particular for readers
who are less familiar with compiler/JIT optimizations. However,
section 4 starts with "yet another example" - at least this was my
impression when reading it. I understand the differences and
everything, but still, you might consider to improve the transition
between sections 3 and 4.
}

@@

\revc{
In general, the paper is over-long on generalities and too short on details.
For example, the description of the basic technique at the beginning of section
5 is the third time the idea is explained at basically the same level of detail
(the others are in section 2 and section 4).  In contrast, the optimizations
applied rely on a simple type analysis, but this is only briefly alluded to.
}

@@

\revc{
This paper presents an elegant, if simple, technique, and demonstrates that
it's effective in small cases.  The worked example is particularly helpful, and
would be better if it were worked more thoroughly.  Some of the omitted steps
are not entirely obvious, and the paper would be improved by making the
clearer.  In particular, the final program presented on the bottom of page 5,
first column, still has memory access, boxing, and type checks, which the paper
then claims can be removed.  There's enough space to show this.
}

@@

\revb{
A nit: Section 7 says that loop peeling never makes runtime
performance worse, but generating more code can potentially slow
performance. I assume that non-numeric benchmarks show no slowdown in
practice, and that might be worth noting.
}

\revb{
Section 7 also mentions performance improvements for a Prolog
interpreter. Consider adding a brief explanation of the benefit, since
that example stands out as a non-numeric (I assume) performance
improvement.
}

\revc{
Providing source code for the benchmarks measured are needed for others to
reproduce and build on your results.  I believe this should be the minimum
standard for publishing measurements such as these.
}

\revc{
I would have liked to have benchmark results for some larger applications.
When is this optimization effective on a large scale, if ever?
}

\revd{
It isn't clear from the paper, but a reader might conclude that the bulk of the
time savings are from removing boxing/unboxing operations.
}

\revd{
The benchmark results appear quite impressive -- especially the comparison with
GCC -- but without additional information, I have no idea what is being
compared.  Are these results from the same sizes of integers and/or floating
point results?
}

\revd{
This paper is relatively short, and could be significantly improved with a
couple of pages of additional information about the details of the benchmarks
-- both on the Python and on the C side.
}

@@

\revc{
Include the OS with your benchmark specifications.
}

@@

\reva{
First sentence of the related work section is kind of
unfortunate. It is unclear what the reference at the end of the
sentence is good for. To support the meaning of the entire sentence?
Or is it just a reference to the standard loop invariant code motion
techniques? The contribution of your paper seems much smaller than
in the former case compared to the latter one. While I have not
checked the content of the book, I believe the latter is the correct
interpretation. You should remove this opportunity for
misinterpretation.}

@@

\revc{
The discussion of LuaJIT is unsatisfying.  It's not clear to me from that one
quote that Mike is doing the same thing.  It might be worth including LuaJIT in
the benchmarks, and/or examining the actual implementation of LuaJIT.
}
